HTW Hybrid Models

### 2024-03-01 Model/hybrid.qmd
few more big hybrid fits

folder_names <- c("e1_hybrid_n_iter_250_ntry_200_0637",
"e1_hybrid_n_iter_60_ntry_150_2335",
"e1_hybrid_n_iter_200_ntry_300_0741",
"e1_hybrid_n_iter_150_ntry_150_4749","e1_hybrid_n_iter_100_ntry_100_1435")

>>>>

folder_names <- c("e1_hybrid_n_iter_250_ntry_200_0637",
"e1_hybrid_n_iter_60_ntry_150_2335",
"e1_hybrid_n_iter_200_ntry_300_0741",
"e1_hybrid_n_iter_150_ntry_150_4749","e1_hybrid_n_iter_100_ntry_100_1435","e1_hybrid_n_iter_400_ntry_300_3744")
